---
title: "Housing Fluctuation using Case-Shiller Index"
description: |
  This project is about observing and analysing the housing fluctuation of an single familly house from 1987 to Janurary 2021 of three cities: Boston, New York City and San Francisco. 
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(lubridate)
library(dplyr)
library(plotly)
library(gganimate)
library(gifski)
library(png)
library(patchwork)
library(gapminder)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

# Learn more about publishing to GitHub Pages at:
# https://rstudio.github.io/distill/publish_website.html#github-pages
```

# Housing Fluctuation #
```{r}

raw_housing_BO <- read.csv("BOXRSA.csv")
raw_housing_NY <- read.csv("NYXRSA.csv")
raw_housing_SF <- read.csv("SFXRSA.csv")
raw_housing_COM <- read.csv("SPCS20RSA.csv")

housing_BO <- raw_housing_BO %>%
mutate(City="Boston") %>%
mutate(Data_housing= BOXRSA)

housing_NY <- raw_housing_NY %>%
  mutate(City="New York")%>%
  mutate(Data_housing= NYXRSA)

housing_SF <- raw_housing_SF %>%
  mutate(City ="San Francisco")%>%
mutate(Data_housing= SFXRSA)

housing_COM <- raw_housing_COM %>%
mutate(City="Case-Shiller Composite") %>%
mutate(Data_housing= SPCS20RSA)

clean_housing_data <-bind_rows(housing_BO,housing_NY,housing_SF,housing_COM)
```

```{r,echo=FALSE}
data_housing_final <- clean_housing_data %>%
select(DATE,Data_housing,City)%>%
  group_by(City) 
```

```{r}
data_housing_plotly <- data_housing_final%>%
ggplot(mapping=aes(x = DATE,y=Data_housing,color=City,group=1, text = paste("Date:",DATE, "\n")))+
  geom_line()+
  scale_x_discrete(breaks=12)+
  labs(title="Housing Price Fluctuation of Three Major Cities In US",x="Time (2000-2021)",y="Case-Shiller Housing Price Index")

   ggplotly(data_housing_plotly, tooltip = "text")
     
```

# Metropolitan Population #
```{r}
raw_pop_BO <- read.csv("BOSPOP.csv")
raw_pop_NY <- read.csv("NYTPOP.csv")
raw_pop_SF <- read.csv("SFCPOP.csv")

pop_BO <- raw_pop_BO %>%
mutate(City="Boston") %>%
mutate(Data_pop= BOSPOP)

pop_NY <- raw_pop_NY %>%
  mutate(City="New York")%>%
  mutate(Data_pop= NYTPOP)

pop_SF <- raw_pop_SF %>%
  mutate(City ="San Francisco")%>%
mutate(Data_pop= SFCPOP)

clean_pop_data <-bind_rows(pop_BO,pop_NY,pop_SF)
```

```{r,echo=FALSE}
data_pop_final <- clean_pop_data %>%
select(DATE,Data_pop,City)%>%
  group_by(City) 
```

```{r}
data_pop_plotly <- data_pop_final%>%
ggplot(mapping=aes(x = DATE,y=Data_pop,color=City,group=1, text = paste("Date:",DATE, "\n")))+
  geom_line()+
  scale_x_discrete(breaks=12)+
  labs(title="Population of Three Major Cities in US Overtime",x="Time (2000-2020)",y="Metro Population In Thousands")

   ggplotly(data_pop_plotly, tooltip = "text")
     
```

# Real Median Income #
```{r}
raw_Income_MA <- read.csv("MedianIncomeMA.csv")
raw_Income_NY <- read.csv("MedianIncomeNY.csv")
raw_Income_CA <- read.csv("MedianIncomeCA.csv")
raw_Income_USA <- read.csv("MedianIncomeUSA.csv")

Income_MA <- raw_Income_MA %>%
mutate(States="Massachusetts") %>%
mutate(Data_Income=MEHOINUSMAA672N)

Income_NY <- raw_Income_NY %>%
  mutate(States="New York")%>%
  mutate(Data_Income= MEHOINUSNYA672N)

Income_CA <- raw_Income_CA %>%
  mutate(States ="California")%>%
mutate(Data_Income=MEHOINUSCAA672N)

Income_USA <- raw_Income_USA %>%
mutate(States="United States") %>%
mutate(Data_Income=MEHOINUSA672N)

clean_Income_data <-bind_rows(Income_MA,Income_NY,Income_CA,Income_USA)
```

```{r,echo=FALSE}
data_Income_final <- clean_Income_data %>%
select(DATE,Data_Income,States)%>%
  group_by(States) 
```

```{r}
data_Income_plotly <- data_Income_final%>%
ggplot(mapping=aes(x = DATE,y=Data_Income,color=States,group=1, text = paste("Date:",DATE, "\n")))+
  geom_line()+
  scale_x_discrete(breaks=12)+
  labs(title="Real Median Household Income Of Three Cities",x="Time (2000-2020)",y="US Adjusted Dollar")

   ggplotly(data_Income_plotly, tooltip = "text")
     
```

```{r}
housing_supply_USA <- read_csv("MSACSR.csv")

supply_plotly <- housing_supply_USA%>%
ggplot(mapping=aes(x = DATE,y=MSACSR,group=1, text = paste("Date:",DATE, "\n")))+
  geom_line()+
  labs(title = "Monthly Supply of Houses in the United States",x= "Date(2000-2021)",y="Month's Supply")

ggplotly(supply_plotly, tooltip = "text")
```

# Analysis #

### Analysis Graph 1 ###
San Francisco endured the greatest decline in 2008 Housing bubble, as well as the greatest increased after the crash,much higher than the Case-Shiller 20 City Composite which measures the average housing values of 20 major cities in the US, and for all three cities housing price shows an upward sloping trend, which means that the value of an single-family house keep increasing over time. 


### Analysis Graph 2 ###
By comparing the first graph and the second, it seems like population is not an factor on housing as San Francisco does not have an greater population than New York City and Boston, and it seems like it doesn't have an huge increase in population than the other two cities, we can conclude by saying population is not an major factor that determine the housing Price. 

### Analysis Graph 3 ###
Comparing the first graph and the third, we can say that income is one of the factors that influenced the Housing Price as the ups and downs of the Income graph matched up with the Housing graph. 

### Analysis Graph 4 ###
This graph represent the general "Supply" curve for housing price, comparing the first graph and this graph we can see that the price follows general models of supply and demand curve in economics, where more supply less demand means price decrease, less supply more demand means price increase. 



